<style type="text/css">
/*  CSS chunck 1  */
th{ background-color:#E0E0E0 ; border-bottom:1px solid black; padding:4px;}
td{ border-bottom:1px dotted black; padding:5px;}
table{ border-collapse:collapse; margin:auto; border: 1px solid black;}
table td { border-left: 1px solid #000; border-right: 1px solid #000; }
table td:first-child { border-left: none; }
table td:last-child { border-right: none; }
table, th, td {
        font-family: Consolas, 'Helvetica Neue', Helvetica, Calibri;
}
body {
  ##margin: auto;
  margin-left:30px;
  width:90%; 
  font-family: Consolas, 'Helvetica Neue', Helvetica, Calibri;
  font-size: 14px;
  line-height: 18px;
  color: #333333;
  background-color: #ffffff;
}
</style>

```{r setup,echo=FALSE}
library(knitr)
opts_chunk$set(
  fig.path=paste0(fig.path, "/"), 
  fig.align='left', 
  comment="",
  echo=FALSE, 
  warning=FALSE, 
  error=TRUE, 
  message=FALSE, 
  cache=FALSE, 
  dpi=100,
  ##dev=c("svg", "png", "pdf", "postscript"),
  dev="svg",
  results="asis")
options(knitr.table.format = 'html')
```

# `r basename(args$dataDir)` attrition table
`r format(Sys.Date(), "%b %d %Y")`

### Things to look for

- The plots are in log scale, so the attrition table should look smooth.
- Normally there are 4 replicates for each GTSP, check the variations between replicates.

### GTSP summary information
```{r gtspTable, results="asis"}
##kable(gtspInfo, caption="GTSP-patient", row.names=FALSE)

summary <- (stats %>%
                group_by(gtsp) %>%
                    mutate(Reps=n(),
                           allReads=sum(barcoded),
                           trimedR=sum(vTrimed),
                           PEMapped=sum(numProperlyPairedAlignments),
                           single=sum(numAllSingleReads),
                           multi=sum(multihitReads),
                           uSites=sum(numUniqueSites),
                           uSitesAbun=sum(numAllSingleSonicLengths),
                           mClusters=sum(multihitClusters),
                           mAbun=sum(multihitSonicLengths)) %>%
                        select(gtsp, info, Reps, allReads, trimedR, PEMapped,
                               single, multi, uSites, uSitesAbun,
                               mClusters, mAbun) %>%
                            distinct() )

kable(summary, row.names=FALSE)
```

<P style="page-break-before: always">
	
```{r plotList, results='hide'}
plotAttritionList <- function(mdfList, plotsPerPage=2) {
    
    plotList <- list()
    if( length(mdfList)>0 ) {
        plotList <- split(1:length(mdfList), (1:length(mdfList)-1)%/%2)
    }

    null <- sapply(seq(plotList), function(i) {
        breaks = 10**(1:10)
    
        p <- ggplot(plyr::rbind.fill(mdfList[ plotList[[i]] ]), 
                    aes(variable, value, fill=Replicate)) +
            geom_bar(position=position_dodge(width = 0.8), stat="identity") + 
            ##scale_y_log10() +
            scale_y_log10(breaks = breaks, labels = comma(breaks)) +
            ##coord_flip() +
            geom_vline(xintercept = 1:(nlevels(stats.mdf$variable)-1)+0.5, linetype=4) +
            theme_default() +
            facet_wrap( ~ gtspinfo, ncol=1, scales = "free_y")
        print(p)
        cat("<hr>", "\n")
        cat("<P style=\"page-break-before: always\">", "\n")
    } )
}
```


### Control or other samples
```{r controlstats, fig.width=8, fig.height=10, results='asis'}
## samples named not like GTSP0001, usually controls
mdfList <- subset(stats.mdf.listBygtsp,
                  ! grepl("GTSP", names(stats.mdf.listBygtsp)))

plotAttritionList(mdfList)
```
	
### GTSP samples
```{r gtspstats, fig.width=8, fig.height=10, results='asis'}
## seperate samples named like GTSP0001, normally real samples
mdfList <- subset(stats.mdf.listBygtsp,
                  grepl("GTSP", names(stats.mdf.listBygtsp)))
plotAttritionList(mdfList)
```

